The problem and promise of scale in animal social multilayer networks

### 2020-08-27 paper/manuscript.Rmd
minor edits

Habitat selection, the use of available resources or landscape features by
animals [@Manly_1993; @Boyce_1999], is a scale-dependent process [@Mayor_2009]
that we can observe in multilayer networks.
Social structure and habitat selection are intimately related and individuals
must share space to interact [@Webber_2018]. We found edge overlap was stable in
open and forest layers but decreased in foraging layers as spatial
scale increased (Figure \@ref(fig:lcres) D). Graph strength had greater individual
variation in open and foraging layers than in forest layers (Figure
\@ref(fig:lcres) E). Furthermore, we observed a decrease in the proportion of relocations in
foraging habitat with increasing spatial resolution 
(`r count[res == 30 & lc == 3, percent]`% at 30 m - `r count[res == 1000 & lc == 3, percent]`% at 1000
m). As the foraging layer had similar edge overlap and graph strength as the
open layer at 30 m spatial resolution, spatial scale therefore played a
key role in our multilayer social networks. 
Johnson [-@Johnson_1980] identified four orders, or scales,  of habitat selection: (1) the
geographical range of a species, (2) the home range of an individual, the (3)
habitat patches within the home range and (4) specific resources within a
habitat patch. Scales of habitat selection could be relevant for multilayer networks and our
integration of habitat within a multilayer context could be an important first
step. Specifically, if individuals select habitats
at the home range scale - e.g. at coarser resolution, it may be relevant to assess social structure using
home range overlap. By contrast, in cases where individuals select habitats at
the patch-scale, fine-scale measures of sociality may be more relevant. Moving
past this hierarchical perspective, Mayor et al. [-@Mayor_2007] emphasized the
importance of considering a broad continuum of scales to reveal scale-dependent
selection and avoid the bias of predefined scales assumed to associate with
certain behaviours. We highlight the concept of scale in multilayer 
networks should be approached based on explicit and precise definitions
to ensure robust measurements.

@@

1. How do multilayer social network metrics vary across social, spatial, and temporal scales and
at which scale might these influence fitness (Box 1)? Are some scales better predictors
for different fitness components, e.g. reproductive success or suvival?

2. Why do individuals associate more strongly with certain conspecifics in some
habitats? What is the role of movement in the context of habitat
networks?

>>>>

Habitat selection, the use of available resources or landscape features by
animals [@Manly_1993; @Boyce_1999], is a scale-dependent process [@Mayor_2009]
that we can observe in multilayer networks.
Social structure and habitat selection are intimately related and individuals
must share space to interact [@Webber_2018]. We found edge overlap was stable in
open and forest layers but decreased in foraging layers as spatial
scale increased (Figure \@ref(fig:lcres) D). Graph strength had greater individual
variation in open and foraging layers than in forest layers (Figure
\@ref(fig:lcres) E). On average, graph strength was highest in foraging habitat, 
compared to forest and open habitat, despite the fact that foraging habitat was 
the least common. Furthermore, we observed a decrease in the proportion of relocations in
foraging habitat with increasing spatial resolution 
(`r count[res == 30 & lc == 3, percent]`% at 30 m - `r count[res == 1000 & lc == 3, percent]`% at 1000
m). As the foraging layer had similar edge overlap and graph strength as the
open layer at 30 m spatial resolution, spatial scale therefore played a
key role in our multilayer social networks. 
Johnson [-@Johnson_1980] identified four orders, or scales,  of habitat selection: (1) the
geographical range of a species, (2) the home range of an individual, the (3)
habitat patches within the home range and (4) specific resources within a
habitat patch. Scales of habitat selection could be relevant for multilayer networks and our
integration of habitat within a multilayer context could be an important first
step. Specifically, if individuals select habitats
at the home range scale - e.g. at coarser resolution, it may be relevant to assess social structure using
home range overlap. By contrast, in cases where individuals select habitats at
the patch-scale, fine-scale measures of sociality may be more relevant. Moving
past this hierarchical perspective, Mayor et al. [-@Mayor_2007] emphasized the
importance of considering a broad continuum of scales to reveal scale-dependent
selection and avoid the bias of predefined scales assumed to associate with
certain behaviours. We highlight the concept of scale in multilayer 
networks should be approached based on explicit and precise definitions
to ensure robust measurements.

@@

1. How do multilayer social network metrics vary across social, spatial, and temporal scales and
at which scale might these influence fitness (Box 1)? Are some scales better predictors
for different fitness components, e.g. reproductive success or survival?

2. Why do individuals associate more strongly with certain conspecifics in some
habitats? What is the role of movement in the context of habitat-specific social
networks?
